State of the Practice for Lattice Boltzmann Method Software

### 2022-03-26 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
no solo tables; table 4 column reordering

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{5.5cm} }
			\toprule
			Name & Released & Updated & Relevant Publication\\
			\midrule
			\href{https://www.ccp5.ac.uk/sites/www.ccp5.ac.uk/files/dl_meso/data/dl_meso_2.7.zip}{DL\_MESO (LBE)} & unclear & 2020 Mar&\citep{seaton2013dlmeso}\\
			\href{https://github.com/espressomd/espresso}{ESPResSo} & 2010 Nov & 2020 Jun&\citep{weik2019espresso}\\
			\href{https://github.com/espressopp/espressopp}{ESPResSo++} & 2011 Feb & 2020 Apr&\citep{halverson2013espresso++}\\
			\href{https://github.com/mabau/lbmpy}{lbmpy}& unclear  & 2020 Jun & \citep{bauer2021lbmpy}\\
			\href{https://github.com/Olllom/lettuce}{lettuce} & 2019 May & 2020 Jul&\citep{bedrunka2021lettuce}\\
			\href{https://github.com/ludwig-cf/ludwig}{Ludwig} & 2018 Aug & 2020 Jul&\citep{desplat2001ludwig}\\
			\href{https://github.com/aharwood2/LUMA}{LUMA} & 2016 Nov   & 2020 Feb &\citep{harwood2018luma}\\
			\href{http://hg.savannah.gnu.org/hgweb/mechsys/file/tip/}{MechSys} & 2008 Jun    & 2021 Oct &\citep{galindo2013coupled}\\
			\href{https://osdn.net/projects/apes/scm/hg/musubi/}{Musubi} & 2013 Sep & 2019 Aug &\citep{hasert2014complex}\\
			\href{https://www.openlb.net/download/}{OpenLB} & 2007 Jul & 2019 Oct &\citep{heuveline2010openlb}\\
			\href{https://gitlab.com/unigespc/palabos}{Palabos} & unclear & 2020 Jul &\citep{latt2021palabos}\\
			\href{https://github.com/pylbm/pylbm}{pyLBM} & 2015 Jun&   2020 Jun &\\
			\href{https://github.com/sailfish-team/sailfish}{Sailfish} & 2012 Nov & 2019 Jun & \citep{januszewski2014sailfish}\\
			\href{https://github.com/CFD-GO/TCLB}{TCLB} & 2013 Jun  & 2020 Apr & \citep{rokicki2016adjoint}\\
			\href{https://i10git.cs.fau.de/walberla/walberla}{waLBerla} & 2008 Aug & 2020 Jul & \citep{bauer2021walberla}\\
			\bottomrule
		\end{tabular}
		\caption{Alive Software Packages} \label{alivepackages}
	\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{5.5cm} }
			\toprule
			Name & Released & Updated & Relevant Publication\\
			\midrule
			\href{https://github.com/UCL/hemelb}{HemeLB} & 2007 Jun & 2018 Aug&\citep{mazzeo2008hemelb}\\
			\href{https://github.com/maxlevesque/laboetie}{laboetie} & 2014 Nov & 2018 Aug&\citep{levesque2013accounting}\\		
			\href{https://github.com/UCL/LatBo.jl}{LatBo.jl} & 2014 Aug & 2017 Feb&\\
			\href{https://code.google.com/p/lb2d-prime-dev/source}{LB2D-Prime} & 2005 & 2012 Apr&\\
			\href{http://ccs.chem.ucl.ac.uk/sites/ccs.chem.ucl.ac.uk/themes/ccs2/files/lb3d-2012-03-12.tgz}{LB3D} & unclear & 2012 Mar&\citep{schmieschek2017lb3d}\\
			\href{https://code.google.com/archive/p/lb3d-prime-dev/source}{LB3D-Prime} & 2005 & 2011 Oct&\\
			\href{https://code.google.com/archive/p/limbes/source}{LIMBES} & 2010 Nov & 2014 Dec&\\
			\href{https://github.com/carlosrosales/mplabs}{MP-LABS} & 2008 Jun & 2014 Oct&\\
			\href{https://sourceforge.net/projects/sunlightlb/files/latest/download}{SunlightLB} & 2005 Sep & 2012 Nov&\\
			\bottomrule
		\end{tabular}
		\caption{Dead Software Packages} \label{deadpackages}
	\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}llllllll}
			\toprule
			Name & Dim & Pll & Com & Rflx & MFl & Turb & CGE & OS\\
			\midrule
			DL\_MESO (LBE) & 2, 3 & MPI/OMP & Y & Y & Y & Y & Y & W, M, L\\
			ESPResSo & 1, 2, 3 & CUDA/MPI & Y & Y & Y & Y & Y & M, L\\
			ESPResSo++ & 1, 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			HemeLB & 3 & MPI & Y & Y & Y & Y & Y & L\\
			laboetie & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			LatBo.jl & 2, 3 & - & Y & Y & Y & N & Y & L\\
			LB2D-Prime & 2 & MPI & Y & Y & Y & Y & Y & W, L\\
			LB3D & 3 & MPI & N & Y & Y & Y & Y & L\\
			LB3D-Prime & 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			lbmpy & 2, 3 & CUDA & Y & Y & Y & Y & Y & L\\
			lettuce & 2, 3 & CUDA & Y & Y & Y & Y & Y & W, M, L\\
			LIMBES & 2 & OMP & Y & Y & N & N & Y & L\\
			Ludwig & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			LUMA & 2, 3 & MPI & Y & Y & Y & Y & Y & W, M, L\\
			MechSys & 2, 3 & - & Y & Y & Y & Y & Y & L\\
			MP-LABS & 2, 3 & MPI/OMP & N & Y & Y & N & N & L\\
			Musubi & 2, 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			OpenLB & 1, 2, 3 & MPI & Y & Y & Y & Y & Y & W, M, L\\
			Palabos & 2, 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			pyLBM & 1, 2, 3 & MPI & Y & Y & N & Y & Y & W, M, L\\
			Sailfish & 2, 3 & CUDA & Y & Y & Y & Y & Y & M, L\\
			SunlightLB & 3 & - & Y & Y & N & N & Y & L\\
			TCLB & 2, 3 & CUDA/MPI & Y & Y & Y & Y & Y & L\\
			waLBerla & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			\bottomrule
		\end{tabular}
		\caption{Features of Software Packages (Dim for Dimension (1, 2, 3), Pll
			for Parallel (CUDA, MPI, OpenMP (OMP)), Com for Compressible (Yes or
			No), Rflx for Reflexive Boundary Condition (Yes or No), MFl for
			Multi-fluid (Yes or No), Turb for Turbulent (Yes or No), CGE for
			Complex Geometries (Yes or No), OS for Operating System (Windows
			(W), macOS (M), Linux (L)))} \label{tbl_features}
	\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{3.5cm}p{3.5cm}p{2.5cm} }
			\toprule
			Name & $\%$ Issues Closed & $\%$ Code Comments & Status\\
			\midrule
			MP-LABS & 100.00 & 26.67 & Dead\\
			Musubi & Not Git & 24.19 & Alive\\
			waLBerla & 72.90 & 22.62 & Alive\\
			OpenLB & Not Git & 22.43 & Alive\\
			ESPResSo & 89.26 & 21.78 & Alive\\
			Ludwig& 60.00 & 20.70 & Alive\\
			Palabos & 89.47 & 17.76 & Alive\\
			SunlightLB & Not Git & 17.67 & Dead\\
			LIMBES & Not Git & 17.39 & Dead\\
			ESPResSo++ & 66.28 & 17.10 & Alive\\
			HemeLB & No Issues & 16.68 & Dead\\
			pyLBM & 66.67& 16.12 & Alive\\
			MechSys & Not Git & 15.11 & Alive\\
			LB3D-Prime & Not Git & 14.34 & Dead\\
			LB3D & Not Git & 13.76 & Dead\\
			LB2D-Prime & Not Git & 13.61 & Dead\\
			Sailfish & 22.22 & 9.26 & Alive\\
			lettuce & 33.33 & 8.19 & Alive\\
			DL\_MESO (LBE) & Not Git & 8.06& Alive\\
			TCLB & 60.32 & 6.02 & Alive\\
			laboetie & 18.75 & 2.47 & Dead\\	
			lbmpy& 58.33  & 2.03 & Alive\\	
			LatBo.jl & 93.33 & 0.40 & Dead\\
			LUMA& 85.71   & 0.20 & Alive\\
			\bottomrule
		\end{tabular}
		\caption{Git Repository Data, Sorted by Percentage of Code that is
		Comments} \label{gitrepodata}
	\end{center}
	\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{2cm}p{2.5cm}p{2cm}p{2.5cm} }
			\toprule
			Name & Text Files & Binary Files & LOC & Avg.\ LOC / Text File\\
			\midrule
			LUMA & 314 & 19 & 4399723 & 14011\\
			LatBo.jl & 41& 0 & 42172 & 1029\\
			LB2D-Prime & 82& 19 & 54755 & 668\\
			LB3D-Prime & 23& 6 & 12944 & 563\\
			DL\_MESO (LBE) & 310 & 51 & 170223 & 549\\
			LB3D & 99 & 76 & 39766 & 402\\
			laboetie & 133& 1 & 48403 & 364\\
			waLBerla & 2643 & 69 & 873988 & 331\\
			MechSys & 333 & 3 & 95707 & 287\\
			Palabos & 1974 & 71 & 563841 & 286\\
			lbmpy& 250 & 29 & 61632 & 247\\
			SunlightLB & 36 & 1 & 7646 & 212\\
			Musubi & 1347 & 1839 & 281879 & 209\\
			LIMBES & 26 & 1 & 4872 & 187\\
			Ludwig & 954 & 32 & 162518 & 170\\
			OpenLB & 1438 & 7 & 218406 & 152\\
			ESPResSo & 1390& 83 & 195083 & 140\\
			MP-LABS & 307 & 3 & 43124 & 140\\
			pyLBM & 272 & 108 & 37234 & 137\\
			ESPResSo++ & 1406& 30 & 165194 & 118\\
			HemeLB & 1102& 44 & 123806 & 112\\
			Sailfish & 632 & 11 & 69398 & 110\\
			lettuce & 73 & 1 & 7660 & 105\\
			TCLB & 594 & 7 & 49156 & 83\\
			\bottomrule
		\end{tabular}
		\caption{Module Data} \label{moduledata}
	\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{1.25cm}p{1.75cm}p{1.75cm}p{1.75cm}p{1.75cm} }
			\toprule
			Name & Our Ranking & Repository Stars & Repository Star Rank &
			Repository Watches & Repository Watch Rank\\
			\midrule
			ESPResSo & 1 & 145 & 2 & 19& 2\\
			Ludwig & 2 & 27 & 8 & 6& 7\\
			Palabos & 3 & 34 & 6 & GitLab& GitLab\\
			OpenLB & 4 & No Git & No Git & No Git& No Git\\
			LUMA & 5 & 33 & 7 & 12& 4\\
			pyLBM & 6 & 95 & 3 & 10& 5\\
			DL\_MESO (LBE) & 7 & No Git & No Git & No Git & No Git\\
			Musubi & 8 & No Git & No Git & No Git & No Git\\
			Sailfish & 9 & 186 & 1 & 41& 1\\
			waLBerla & 10 & 20 & 9 & GitLab& GitLab\\
			laboetie & 11 & 4 & 13 & 5& 8\\
			TCLB & 12 & 95 & 3 & 16& 3\\
			MechSys & 13 & No Git & No Git & No Git& No Git\\
			lettuce & 14 & 48 & 4 & 5& 8\\
			ESPResSo++ & 15 & 35 & 5 & 12& 4\\
			MP-LABS & 16 & 12 & 11 & 2& 9\\			
			SunlightLB & 17 & No Git & No Git & No Git& No Git\\
			LB3D & 18 & No Git & No Git & No Git& No Git\\			
			LIMBES & 19 & No Git & No Git & No Git& No Git\\
			LB2D-Prime & 20 & No Git & No Git & No Git& No Git\\		
			HemeLB & 21 & 12 & 11 & 12& 4\\
			lbmpy & 22 &  11 & 12 & 2& 9\\	
			LB3D-Prime & 23 & No Git & No Git & No Git& No Git\\	
			LatBo.jl & 24 & 17 & 10 & 8& 6\\			
			\bottomrule
		\end{tabular}
		\caption{Repository Ranking Metrics} \label{repometrics}
	\end{center}
	\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Issue Tracker & Design Documentation & Developer / Contributor Manual\\
Library Dependency List & Functional Spec. / Notes & FAQ / Forum\\
Installation Guide / Instructions & Performance Information & Verification and
Validation Plan\\
Theory Notes & Test Plan / Script / Cases & Video Guide
(including YouTube)\\
List of Related Publications & User Manual / Guide & Requirements Spec.\\
Makefile / Build File &  & \\
README File & & \\
License & & \\
Tutorial & & \\
Version Control & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
	\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
	\toprule
	\textbf{Development Tools} & \textbf{Dependencies} & \textbf{Project
	Management Tools} \\
	\midrule
	Continuous Integration & Build Automation Tools & Collaboration Tools\\
	Code Editors & Technical Libraries & Email\\
	Development Environments & Domain Specific Libraries & Change Tracking Tools\\
	Runtime Environments &  & Version Control Tools\\
	Compilers &  & Document Generation Tools\\
	Unit Testing Tools &  & \\
	Correctness Verification Tools &  & \\
	\bottomrule
	\end{tabular}
	\caption{Observed development tools, dependencies and project management
	tools} \label{tbl_tools}
	\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3cm}p{1.9cm}p{1.9cm}p{1.9cm}p{1.9cm}p{1.9cm} }
			\toprule
			Quality & Ranked 1st & Ranked 2nd & Ranked 3rd & Ranked 4th & Ranked
			5th\\
			\midrule
			Installability & ESPResSo & MechSys & OpenLB & DL\_MESO (LBE) &
			Sailfish\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface Correctness \\ and Verifiability} & Ludwig &
			Musubi & pyLBM & OpenLB & waLBerla\\
			\addlinespace[0.4cm]
			Surface Reliability & DL\_MESO (LBE) & laboetie* & lettuce & MechSys
			& Musubi \\
			\addlinespace[0.4cm]
			Surface Robustness & DL\_MESO (LBE) & ESPResSo++ & lettuce & LUMA &
			OpenLB \\
			\addlinespace[0.4cm]
			Surface Usability & laboetie* & ESPResSo & OpenLB & Ludwig & Sailfish\\
			\addlinespace[0.4cm]
			Maintainability & Ludwig & MP-LABS* & ESPResSo++ & ESPResSo & Palabos\\
			\addlinespace[0.4cm]
			Reusability & ESPResSo & waLBerla & ESPResSo++ & Sailfish & HemeLB*\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface \\Understandability} & LUMA & Palabos & pyLBM &
			DL\_MESO (LBE)& MechSys\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Visibility and \\Transparency} & Ludwig & Palabos &
			LUMA & ESPResSo & MP-LABS*\\
			\addlinespace[0.4cm]
			Overall Quality & ESPResSo & Ludwig & Palabos & OpenLB & LUMA\\
			\bottomrule
		\end{tabular}
		\caption{Top performers for each quality (all packages were alive at the
		time of measurement, except for those marked by an asterisk (*))}
		\label{topperformerstable}
	\end{center}
\end{table}

>>>>

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{5.5cm} }
			\toprule
			Name & Released & Updated & Relevant Publication\\
			\midrule
			\href{https://www.ccp5.ac.uk/sites/www.ccp5.ac.uk/files/dl_meso/data/dl_meso_2.7.zip}{DL\_MESO (LBE)} & unclear & 2020 Mar&\citep{seaton2013dlmeso}\\
			\href{https://github.com/espressomd/espresso}{ESPResSo} & 2010 Nov & 2020 Jun&\citep{weik2019espresso}\\
			\href{https://github.com/espressopp/espressopp}{ESPResSo++} & 2011 Feb & 2020 Apr&\citep{halverson2013espresso++}\\
			\href{https://github.com/mabau/lbmpy}{lbmpy}& unclear  & 2020 Jun & \citep{bauer2021lbmpy}\\
			\href{https://github.com/Olllom/lettuce}{lettuce} & 2019 May & 2020 Jul&\citep{bedrunka2021lettuce}\\
			\href{https://github.com/ludwig-cf/ludwig}{Ludwig} & 2018 Aug & 2020 Jul&\citep{desplat2001ludwig}\\
			\href{https://github.com/aharwood2/LUMA}{LUMA} & 2016 Nov   & 2020 Feb &\citep{harwood2018luma}\\
			\href{http://hg.savannah.gnu.org/hgweb/mechsys/file/tip/}{MechSys} & 2008 Jun    & 2021 Oct &\citep{galindo2013coupled}\\
			\href{https://osdn.net/projects/apes/scm/hg/musubi/}{Musubi} & 2013 Sep & 2019 Aug &\citep{hasert2014complex}\\
			\href{https://www.openlb.net/download/}{OpenLB} & 2007 Jul & 2019 Oct &\citep{heuveline2010openlb}\\
			\href{https://gitlab.com/unigespc/palabos}{Palabos} & unclear & 2020 Jul &\citep{latt2021palabos}\\
			\href{https://github.com/pylbm/pylbm}{pyLBM} & 2015 Jun&   2020 Jun &\\
			\href{https://github.com/sailfish-team/sailfish}{Sailfish} & 2012 Nov & 2019 Jun & \citep{januszewski2014sailfish}\\
			\href{https://github.com/CFD-GO/TCLB}{TCLB} & 2013 Jun  & 2020 Apr & \citep{rokicki2016adjoint}\\
			\href{https://i10git.cs.fau.de/walberla/walberla}{waLBerla} & 2008 Aug & 2020 Jul & \citep{bauer2021walberla}\\
			\bottomrule
		\end{tabular}
		\caption{Alive Software Packages} \label{alivepackages}
	\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{2cm}p{2cm}p{5.5cm} }
			\toprule
			Name & Released & Updated & Relevant Publication\\
			\midrule
			\href{https://github.com/UCL/hemelb}{HemeLB} & 2007 Jun & 2018 Aug&\citep{mazzeo2008hemelb}\\
			\href{https://github.com/maxlevesque/laboetie}{laboetie} & 2014 Nov & 2018 Aug&\citep{levesque2013accounting}\\		
			\href{https://github.com/UCL/LatBo.jl}{LatBo.jl} & 2014 Aug & 2017 Feb&\\
			\href{https://code.google.com/p/lb2d-prime-dev/source}{LB2D-Prime} & 2005 & 2012 Apr&\\
			\href{http://ccs.chem.ucl.ac.uk/sites/ccs.chem.ucl.ac.uk/themes/ccs2/files/lb3d-2012-03-12.tgz}{LB3D} & unclear & 2012 Mar&\citep{schmieschek2017lb3d}\\
			\href{https://code.google.com/archive/p/lb3d-prime-dev/source}{LB3D-Prime} & 2005 & 2011 Oct&\\
			\href{https://code.google.com/archive/p/limbes/source}{LIMBES} & 2010 Nov & 2014 Dec&\\
			\href{https://github.com/carlosrosales/mplabs}{MP-LABS} & 2008 Jun & 2014 Oct&\\
			\href{https://sourceforge.net/projects/sunlightlb/files/latest/download}{SunlightLB} & 2005 Sep & 2012 Nov&\\
			\bottomrule
		\end{tabular}
		\caption{Dead Software Packages} \label{deadpackages}
	\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}llllllll}
			\toprule
			Name & Dim & Pll & Com & Rflx & MFl & Turb & CGE & OS\\
			\midrule
			DL\_MESO (LBE) & 2, 3 & MPI/OMP & Y & Y & Y & Y & Y & W, M, L\\
			ESPResSo & 1, 2, 3 & CUDA/MPI & Y & Y & Y & Y & Y & M, L\\
			ESPResSo++ & 1, 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			HemeLB & 3 & MPI & Y & Y & Y & Y & Y & L\\
			laboetie & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			LatBo.jl & 2, 3 & - & Y & Y & Y & N & Y & L\\
			LB2D-Prime & 2 & MPI & Y & Y & Y & Y & Y & W, L\\
			LB3D & 3 & MPI & N & Y & Y & Y & Y & L\\
			LB3D-Prime & 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			lbmpy & 2, 3 & CUDA & Y & Y & Y & Y & Y & L\\
			lettuce & 2, 3 & CUDA & Y & Y & Y & Y & Y & W, M, L\\
			LIMBES & 2 & OMP & Y & Y & N & N & Y & L\\
			Ludwig & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			LUMA & 2, 3 & MPI & Y & Y & Y & Y & Y & W, M, L\\
			MechSys & 2, 3 & - & Y & Y & Y & Y & Y & L\\
			MP-LABS & 2, 3 & MPI/OMP & N & Y & Y & N & N & L\\
			Musubi & 2, 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			OpenLB & 1, 2, 3 & MPI & Y & Y & Y & Y & Y & W, M, L\\
			Palabos & 2, 3 & MPI & Y & Y & Y & Y & Y & W, L\\
			pyLBM & 1, 2, 3 & MPI & Y & Y & N & Y & Y & W, M, L\\
			Sailfish & 2, 3 & CUDA & Y & Y & Y & Y & Y & M, L\\
			SunlightLB & 3 & - & Y & Y & N & N & Y & L\\
			TCLB & 2, 3 & CUDA/MPI & Y & Y & Y & Y & Y & L\\
			waLBerla & 2, 3 & MPI & Y & Y & Y & Y & Y & L\\
			\bottomrule
		\end{tabular}
		\caption{Features of Software Packages (Dim for Dimension (1, 2, 3), Pll
			for Parallel (CUDA, MPI, OpenMP (OMP)), Com for Compressible (Yes or
			No), Rflx for Reflexive Boundary Condition (Yes or No), MFl for
			Multi-fluid (Yes or No), Turb for Turbulent (Yes or No), CGE for
			Complex Geometries (Yes or No), OS for Operating System (Windows
			(W), macOS (M), Linux (L)))} \label{tbl_features}
	\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{3.5cm}p{3.5cm}p{2.5cm} }
			\toprule
			Name & $\%$ Code Comments & $\%$ Issues Closed & Status\\
			\midrule
			MP-LABS & 26.67 & 100.00 & Dead\\
			Musubi & 24.19 & Not Git & Alive\\
			waLBerla & 22.62 & 72.90 & Alive\\
			OpenLB & 22.43 & Not Git & Alive\\
			ESPResSo & 21.78 & 89.26 & Alive\\
			Ludwig& 20.70 & 60.00 & Alive\\
			Palabos & 17.76 & 89.47 & Alive\\
			SunlightLB & 17.67 & Not Git & Dead\\
			LIMBES & 17.39 & Not Git & Dead\\
			ESPResSo++ & 17.10 & 66.28 & Alive\\
			HemeLB & 16.68 & No Issues & Dead\\
			pyLBM & 16.12 & 66.67 & Alive\\
			MechSys & 15.11 & Not Git & Alive\\
			LB3D-Prime & 14.34 & Not Git & Dead\\
			LB3D & 13.76 & Not Git & Dead\\
			LB2D-Prime & 13.61 & Not Git & Dead\\
			Sailfish & 9.26 & 22.22 & Alive\\
			lettuce & 8.19 & 33.33 & Alive\\
			DL\_MESO (LBE) & 8.06 & Not Git & Alive\\
			TCLB & 6.02 & 60.32 & Alive\\
			laboetie & 2.47 & 18.75 & Dead\\	
			lbmpy& 2.03 & 58.33 & Alive\\	
			LatBo.jl & 0.40 & 93.33 & Dead\\
			LUMA& 0.20 & 85.71 & Alive\\
			\bottomrule
		\end{tabular}
		\caption{Git Repository Data, Sorted by Percentage of Code that is
			Comments} \label{gitrepodata}
	\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{2cm}p{2.5cm}p{2cm}p{2.5cm} }
			\toprule
			Name & Text Files & Binary Files & LOC & Avg.\ LOC / Text File\\
			\midrule
			LUMA & 314 & 19 & 4399723 & 14011\\
			LatBo.jl & 41& 0 & 42172 & 1029\\
			LB2D-Prime & 82& 19 & 54755 & 668\\
			LB3D-Prime & 23& 6 & 12944 & 563\\
			DL\_MESO (LBE) & 310 & 51 & 170223 & 549\\
			LB3D & 99 & 76 & 39766 & 402\\
			laboetie & 133& 1 & 48403 & 364\\
			waLBerla & 2643 & 69 & 873988 & 331\\
			MechSys & 333 & 3 & 95707 & 287\\
			Palabos & 1974 & 71 & 563841 & 286\\
			lbmpy& 250 & 29 & 61632 & 247\\
			SunlightLB & 36 & 1 & 7646 & 212\\
			Musubi & 1347 & 1839 & 281879 & 209\\
			LIMBES & 26 & 1 & 4872 & 187\\
			Ludwig & 954 & 32 & 162518 & 170\\
			OpenLB & 1438 & 7 & 218406 & 152\\
			ESPResSo & 1390& 83 & 195083 & 140\\
			MP-LABS & 307 & 3 & 43124 & 140\\
			pyLBM & 272 & 108 & 37234 & 137\\
			ESPResSo++ & 1406& 30 & 165194 & 118\\
			HemeLB & 1102& 44 & 123806 & 112\\
			Sailfish & 632 & 11 & 69398 & 110\\
			lettuce & 73 & 1 & 7660 & 105\\
			TCLB & 594 & 7 & 49156 & 83\\
			\bottomrule
		\end{tabular}
		\caption{Module Data} \label{moduledata}
	\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{1.25cm}p{1.75cm}p{1.75cm}p{1.75cm}p{1.75cm} }
			\toprule
			Name & Our Ranking & Repository Stars & Repository Star Rank &
			Repository Watches & Repository Watch Rank\\
			\midrule
			ESPResSo & 1 & 145 & 2 & 19& 2\\
			Ludwig & 2 & 27 & 8 & 6& 7\\
			Palabos & 3 & 34 & 6 & GitLab& GitLab\\
			OpenLB & 4 & No Git & No Git & No Git& No Git\\
			LUMA & 5 & 33 & 7 & 12& 4\\
			pyLBM & 6 & 95 & 3 & 10& 5\\
			DL\_MESO (LBE) & 7 & No Git & No Git & No Git & No Git\\
			Musubi & 8 & No Git & No Git & No Git & No Git\\
			Sailfish & 9 & 186 & 1 & 41& 1\\
			waLBerla & 10 & 20 & 9 & GitLab& GitLab\\
			laboetie & 11 & 4 & 13 & 5& 8\\
			TCLB & 12 & 95 & 3 & 16& 3\\
			MechSys & 13 & No Git & No Git & No Git& No Git\\
			lettuce & 14 & 48 & 4 & 5& 8\\
			ESPResSo++ & 15 & 35 & 5 & 12& 4\\
			MP-LABS & 16 & 12 & 11 & 2& 9\\			
			SunlightLB & 17 & No Git & No Git & No Git& No Git\\
			LB3D & 18 & No Git & No Git & No Git& No Git\\			
			LIMBES & 19 & No Git & No Git & No Git& No Git\\
			LB2D-Prime & 20 & No Git & No Git & No Git& No Git\\		
			HemeLB & 21 & 12 & 11 & 12& 4\\
			lbmpy & 22 &  11 & 12 & 2& 9\\	
			LB3D-Prime & 23 & No Git & No Git & No Git& No Git\\	
			LatBo.jl & 24 & 17 & 10 & 8& 6\\			
			\bottomrule
		\end{tabular}
		\caption{Repository Ranking Metrics} \label{repometrics}
	\end{center}
	\end{table}

@@

\begin{table}[ht!]
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Issue Tracker & Design Documentation & Developer / Contributor Manual\\
Library Dependency List & Functional Spec. / Notes & FAQ / Forum\\
Installation Guide / Instructions & Performance Information & Verification and
Validation Plan\\
Theory Notes & Test Plan / Script / Cases & Video Guide
(including YouTube)\\
List of Related Publications & User Manual / Guide & Requirements Spec.\\
Makefile / Build File &  & \\
README File & & \\
License & & \\
Tutorial & & \\
Version Control & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
	\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
	\toprule
	\textbf{Development Tools} & \textbf{Dependencies} & \textbf{Project
	Management Tools} \\
	\midrule
	Continuous Integration & Build Automation Tools & Collaboration Tools\\
	Code Editors & Technical Libraries & Email\\
	Development Environments & Domain Specific Libraries & Change Tracking Tools\\
	Runtime Environments &  & Version Control Tools\\
	Compilers &  & Document Generation Tools\\
	Unit Testing Tools &  & \\
	Correctness Verification Tools &  & \\
	\bottomrule
	\end{tabular}
	\caption{Observed development tools, dependencies and project management
	tools} \label{tbl_tools}
	\end{center}
\end{table}

@@

\begin{table}[ht!]
	\begin{center}
		\begin{tabular}{ p{3cm}p{1.9cm}p{1.9cm}p{1.9cm}p{1.9cm}p{1.9cm} }
			\toprule
			Quality & Ranked 1st & Ranked 2nd & Ranked 3rd & Ranked 4th & Ranked
			5th\\
			\midrule
			Installability & ESPResSo & MechSys & OpenLB & DL\_MESO (LBE) &
			Sailfish\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface Correctness \\ and Verifiability} & Ludwig &
			Musubi & pyLBM & OpenLB & waLBerla\\
			\addlinespace[0.4cm]
			Surface Reliability & DL\_MESO (LBE) & laboetie* & lettuce & MechSys
			& Musubi \\
			\addlinespace[0.4cm]
			Surface Robustness & DL\_MESO (LBE) & ESPResSo++ & lettuce & LUMA &
			OpenLB \\
			\addlinespace[0.4cm]
			Surface Usability & laboetie* & ESPResSo & OpenLB & Ludwig & Sailfish\\
			\addlinespace[0.4cm]
			Maintainability & Ludwig & MP-LABS* & ESPResSo++ & ESPResSo & Palabos\\
			\addlinespace[0.4cm]
			Reusability & ESPResSo & waLBerla & ESPResSo++ & Sailfish & HemeLB*\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Surface \\Understandability} & LUMA & Palabos & pyLBM &
			DL\_MESO (LBE)& MechSys\\
			\addlinespace[0.4cm]
			\pbox{3.0cm}{Visibility and \\Transparency} & Ludwig & Palabos &
			LUMA & ESPResSo & MP-LABS*\\
			\addlinespace[0.4cm]
			Overall Quality & ESPResSo & Ludwig & Palabos & OpenLB & LUMA\\
			\bottomrule
		\end{tabular}
		\caption{Top performers for each quality (all packages were alive at the
		time of measurement, except for those marked by an asterisk (*))}
		\label{topperformerstable}
	\end{center}
\end{table}
